---
title: " Dressler et al. 2024 Raw Respirometry Analysis"
author: "Terra Dressler"
date: "2024-02-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=FALSE)
```

This RMD contains analysis of raw repirometry data from 4 populations of summer steelhead (Lower Deschutes, John Day, North Umpqua, Siletz) tested in the field during the summers of 2021 and 2022. These data were recorded on FireStingO2 devices.

These data were analyzed using an early version of the package AnalyzeResp developed by Krista Kraskura. The version of the package used for this analysis is included here as the source code. This package has since been deveoped further and can now be found using install.packages("AnalyzeResp). 

The following analysis was completed before the latest development of the package, but since the basic functionality is the same, the following analysis will continue to use the old code sourced here.




#### 1. Load Packages, set source code
```{r}

library(tidyverse)
library(ggplot2)
library(gridExtra)
library(chron)
library(lubridate)
library(dplyr)
library(pryr)
library(ggpubr)
library(magrittr)
library(tidyr)
library(broom)
library(purrr)
library(mclust)
library(chron)
library(DescTools)

source("MR_firesting_v2.1.0_Feb2020.R")
```


#### 2. Metabolic Rate Analysis: Resting Metabolic Rate (RMR)


Lower Deschutes
```{r}

#Note: the rmr2 files for the Ambient treatment start ~240 min in. Since we cut off this first 240min already, I will start only use the rmr2 files in RMR analysis

AUTO_csv_files <- "AUTO/csv_files"

#Ambient treatment 
setwd(AUTO_csv_files)
convert.o2.Firesting(csv.data = "jul25_2022_box2_amb_rmr2.csv", units_from = "pct", units_to = "mg/L", channels = c(1,2,3,4), salinity = 0, atm_pressure = 1018, n_ch = 4)

setwd(AUTO_csv_files)
SMR(data = "jul25_2022_box1_amb_rmr2.csv",
    inventory_data = "inventory_buckhollow.csv",
    cycle_start = 3,
    cycle_end = 10,
    chop_start = 60/60,
    chop_end = 0/60,
   # flush_plot = "OFF",
    date_format = "m/d/y",
    N_Ch=4)  #cleaned! Using ch 1,2,3

setwd(AUTO_csv_files)
SMR(data = "jul25_2022_box2_amb_rmr2.csv",
    inventory_data = "inventory_buckhollow.csv",
    cycle_start = 3,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
   date_format = "m/d/y",
    N_Ch=4, path="UseFolders")  #cleaned! Using ch 1,2,3,4


setwd(AUTO_csv_files)
SMR(data = "jul25_2022_box3_amb_rmr2.csv",
    inventory_data = "inventory_buckhollow.csv",
    cycle_start = 3,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
     date_format = "m/d/y",
    N_Ch=4, path="UseFolders") #cleaned! Using ch 1, 2, 3 (some bad traces in 3, using 0.9 threshold)

Analyzed_files <- "MMR_SMR_AS_EPOC/csv_input_files"

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
 # test = "none",
	data.MMR = "none",
	data.SMR = "jul25_2022_box1_amb_rmr2_analyzed.csv", 
	AnimalID = c("A01","A02", "A03", "A04"),
	BW.animal = c(0.006, 0.0073, 0.0092, 0.0072),
	resp.V = c(2.086, 2.095, 2.089, 2.107), 
	r2_threshold_smr = 0.9,
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4,
	drop_ch = c(4))

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
  test = "none",
	data.MMR = "none",
	data.SMR = "jul25_2022_box2_amb_rmr2_analyzed.csv", 
	AnimalID = c("A05","A06", "A07", "A08"),
	BW.animal = c(0.029, 0.0153, 0.0122, 0.0372),
	resp.V = c(2.095, 2.094, 2.095, 2.089), 
	r2_threshold_smr = 0.9,
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4)


setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
  test = "none",
	data.MMR = "none",
	data.SMR = "jul25_2022_box3_amb_rmr2_analyzed.csv", 
	AnimalID = c("A09","A10", "A11", NA),
		BW.animal = c(0.0442, 0.0239, 0.0072, NA),
	resp.V = c(2.082, 2.088, 2.093, 2.091), 
	r2_threshold_smr = 0.9,
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4,
	drop_ch = c(4))


#Climate treatment


convert.o2.Firesting(csv.data = "jul26_2022_box1_hot_rmr.csv", units_from = "pct", units_to = "mg/L", channels = c(1,2,3,4), salinity = 0, atm_pressure = 1018, n_ch = 4) #copy to csv_files and change name to make compatible for inventory

setwd(AUTO_csv_files)
SMR(data = "jul26_2022_box1_hot_rmr.csv",
    inventory_data = "inventory_buckhollow.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
     date_format = "m/d/y",
    N_Ch=4, path="UseFolders") #cleaned!

setwd(AUTO_csv_files)
SMR(data = "jul26_2022_box2_hot_rmr.csv",
    inventory_data = "inventory_buckhollow.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders") #cleaned!

setwd(AUTO_csv_files)
SMR(data = "jul26_2022_box3_hot_rmr.csv",
    inventory_data = "inventory_buckhollow.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders") #cleaned!


setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
  test = "none",
	data.MMR = "none",
	data.SMR = "jul26_2022_box1_hot_rmr_analyzed.csv", 
	AnimalID = c("H01","H02", "H03", "H04"),
	BW.animal = c(0.0199, 0.0138, 0.0115, 0.0133),
	resp.V = c(2.086, 2.095, 2.089, 2.107), 
	r2_threshold_smr = 0.9,
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4)

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
  test = "none",
	data.MMR = "none",
	data.SMR = "jul26_2022_box2_hot_rmr_analyzed.csv", 
	AnimalID = c("H05","H06", "H07", "H08"),
	BW.animal = c(0.0119, 0.0079, 0.0089, 0.01),
	resp.V = c(2.095, 2.094, 2.095, 2.089), 
	r2_threshold_smr = 0.9,
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4)

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
  test = "none",
	data.MMR = "none",
	data.SMR = "jul26_2022_box3_hot_rmr_analyzed.csv", 
	AnimalID = c("H09","H10", "H11", NA),
		BW.animal = c(0.0094, 0.0075, 0.0118, NA),
	resp.V = c(2.082, 2.088, 2.093, 2.091), 
	r2_threshold_smr = 0.9,
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4,
	drop_ch = c(4))

setwd(AUTO_csv_files)
SMR(data = "jul27_2022_box1_rmr_imd.csv",
    inventory_data = "inventory_buckhollow.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders") #cleaned! 

setwd(AUTO_csv_files)
SMR(data = "jul27_2022_box2_imd_rmr.csv",
    inventory_data = "inventory_buckhollow.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders") #cleaned! electrical or some other issues in the night, many traces unusable

setwd(AUTO_csv_files)
SMR(data = "jul27_2022_box3_imd_rmr.csv",
    #inventory_data =,
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 30/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders")


setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
  test = "none",
	data.MMR = "none",
	data.SMR = "jul27_2022_box1_rmr_imd_analyzed.csv", 
	AnimalID = c("I01","I02", "I03", "I04"),
	BW.animal = c(0.0484, 0.0167, 0.0264, 0.0192),
	resp.V = c(2.086, 2.095, 2.089, 2.107), 
r2_threshold_smr = 0.9,
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4)


setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
  test = "none",
	data.MMR = "none",
	data.SMR = "jul27_2022_box2_imd_rmr_analyzed.csv", 
	AnimalID = c("I05","I06", "I07", "I08"),
	BW.animal = c(0.0244, 0.0125, 0.0085, 0.0082),
	resp.V = c(2.095, 2.094, 2.095, 2.089), 
	r2_threshold_smr = 0.9,
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4)

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
  test = "none",
	data.MMR = "none",
	data.SMR = "jul27_2022_box3_imd_rmr_analyzed.csv", 
	AnimalID = c("I09","I10", "I11", NA),
	BW.animal = c(0.0064, 0.0091, 0.009, NA),
	resp.V = c(2.082, 2.088, 2.093, 2.091), 
  r2_threshold_smr = 0.9,
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4,
	drop_ch = c(4))



```

John Day
```{r}

#Ambient Treatment - Round 1

#No fish will be used from Box 1

setwd(AUTO_csv_files)
SMR(data = "jul12_box2_rmr_18.csv",
    inventory_data = "inventory_bridge.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 60/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders")

#Channels 3 and 4 only

setwd(AUTO_csv_files)
SMR(data = "jul12_box3_rmr_18.csv",
    inventory_data = "inventory_bridge.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start =30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders")

#Channels 2 and 3 only

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
	data.MMR = "none",
	data.SMR = "jul12_box2_rmr_18_analyzed.csv", 
	AnimalID = c(NA,NA, "A105", "A106"),
	BW.animal = c(NA,NA,.055,0.0591),
	resp.V = c(2.079, 2.082, 2.074, 2.106), 
	r2_threshold_smr = 0.9,
	path = "foldering",
	date_format = "y/m/d",
	N_Ch = 4,
	drop_ch = c(1,2))


setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
	data.MMR = "none",
	data.SMR = "jul12_box3_rmr_18_analyzed.csv", 
	AnimalID = c("A107","A108", "A109", "A110"),
	BW.animal = c(0.0241,0.0395,0.0533,0.0321),
	resp.V = c(2.126, 2.060, 2.07, 2.070), 
	r2_threshold_smr = 0.9,
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4,
	drop_ch = c(1, 4))

#Ambient Treatment - Round 2

setwd(AUTO_csv_files)
SMR(data = "jul14_box1_rmr_18.csv",
    inventory_data = "inventory_bridge.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 60/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders")

#Channel 1 is background

setwd(AUTO_csv_files)
SMR(data = "jul14_box2_rmr_18.csv",
    inventory_data = "inventory_bridge.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders")

setwd(AUTO_csv_files)
SMR(data = "jul14_box3_rmr_18.csv",
    inventory_data = "inventory_bridge.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders")

#Omitting channel 2 


setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
	data.MMR = "none",
	data.SMR = "jul14_box1_rmr_18_analyzed.csv", 
	AnimalID = c(NA,"A201", "A202", "A203"),
	BW.animal = c(NA,0.0449,.0298,0.0332),
	resp.V = c(2.074, 2.075, 2.064, 2.076), 
	r2_threshold_smr = 0.9,
	r2_threshold_mmr = 0.9,
	recovMMR_threshold = 0.5,
	min_length_mmr = 120, 
	background_prior = NA,
	background_post = NA, 
	background_slope = NULL,
	background.V = NULL,
	MLND = FALSE,
	match_background_Ch = FALSE,
	mmr_background = "SAME_slope",
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4,
	drop_ch = c(1))

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
	data.MMR = "none",
	data.SMR = "jul14_box2_rmr_18_analyzed.csv", 
	AnimalID = c("A204","A205", "A206", "A207"),
	BW.animal = c(0.0364,.0274,0.0213, 0.0326),
	resp.V = c(2.079, 2.082, 2.074, 2.106), 
	r2_threshold_smr = 0.9,
	r2_threshold_mmr = 0.9,
	recovMMR_threshold = 0.5,
	min_length_mmr = 60, 
	background_prior = NA,
	background_post = NA, 
	background_slope = NULL,
	background.V = NULL,
	MLND = FALSE,
	match_background_Ch = FALSE,
	mmr_background = "SAME_slope",
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4)

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
	data.MMR = "none",
	data.SMR = "jul14_box3_rmr_18_analyzed.csv", 
	AnimalID = c("A208","A209", NA,"A210"),
	BW.animal = c(0.037,0.0189,NA,0.0562),
	resp.V = c(2.126, 2.060, NA, 2.070), 
	r2_threshold_smr = 0.9,
	r2_threshold_mmr = 0.9,
	recovMMR_threshold = 0.5,
	min_length_mmr = 60, 
	background_prior = NA,
	background_post = NA, 
	background_slope = NULL,
	background.V = NULL,
	MLND = FALSE,
	match_background_Ch = FALSE,
	mmr_background = "SAME_slope",
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 3,
	drop_ch = c(2,3))

#20-24 Treatment

setwd(AUTO_csv_files)
SMR(data = "jul15_box1_rmr_22.csv",
    inventory_data = "inventory_bridge.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 60/60,
    chop_end = 20/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders")

setwd(AUTO_csv_files)
SMR(data = "jul15_box2_rmr_22.csv",
    inventory_data = "inventory_bridge.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 60/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders")

setwd(AUTO_csv_files)
SMR(data = "jul15_box3_rmr_22.csv",
    inventory_data = "inventory_bridge.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders")

#Channel 4 did not work, omitting

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
	data.MMR = "none",
	data.SMR = "jul15_box1_rmr_22_analyzed.csv", 
	AnimalID = c(NA,"2201", "2202", "2203"),
	BW.animal = c(NA, 0.052, 0.0575, 0.0549),
	resp.V = c(2.074, 2.075, 2.064, 2.076), 
	r2_threshold_smr = 0.9,
	r2_threshold_mmr = 0.9,
	recovMMR_threshold = 0.5,
	min_length_mmr = 60, 
	background_prior = NA,
	background_post = NA, 
	background_slope = NULL,
	background.V = NULL,
	MLND = FALSE,
	match_background_Ch = FALSE,
	mmr_background = "SAME_slope",
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4,
	drop_ch = c(1))

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
	data.MMR = "none",
	data.SMR = "jul15_box2_rmr_22_analyzed.csv", 
	AnimalID = c("2204","2205", "2206", "2207"),
	BW.animal = c(0.0446, 0.045, 0.0314, 0.0296),
	resp.V = c(2.079, 2.082, 2.074, 2.106), 
	r2_threshold_smr = 0.9,
	r2_threshold_mmr = 0.9,
	recovMMR_threshold = 0.5,
	min_length_mmr = 60, 
	background_prior = NA,
	background_post = NA, 
	background_slope = NULL,
	background.V = NULL,
	MLND = FALSE,
	match_background_Ch = FALSE,
	mmr_background = "SAME_slope",
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4)

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
	data.MMR = "none",
	data.SMR = "jul15_box3_rmr_22_analyzed.csv", 
	AnimalID = c("2208","2209", NA,"2210"),
	BW.animal = c(0.0309, 0.0262, NA, 0.0254),
	resp.V = c(2.126, 2.060, NA, 2.070), 
	r2_threshold_smr = 0.9,
	r2_threshold_mmr = 0.9,
	recovMMR_threshold = 0.5,
	min_length_mmr = 60, 
	background_prior = NA,
	background_post = NA, 
	background_slope = NULL,
	background.V = NULL,
	MLND = FALSE,
	match_background_Ch = FALSE,
	mmr_background = "SAME_slope",
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 3,
	drop_ch = c(3, 4))


#Hot treatment

setwd(AUTO_csv_files)
SMR(data = "jul13_box1_rmr_26.csv",
    inventory_data = "inventory_bridge.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start =30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders")

setwd(AUTO_csv_files)
SMR(data = "jul13_box2_rmr_26.csv",
    inventory_data = "inventory_bridge.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start =30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders")

setwd(AUTO_csv_files)
SMR(data = "jul13_box3_rmr_26.csv",
    inventory_data = "inventory_bridge.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start =30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders")

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
	data.MMR = "none",
	data.SMR = "jul13_box1_rmr_26_analyzed.csv", 
	AnimalID = c(NA,"2601", "2602", "2603"),
	BW.animal = c(NA,0.0348,.0789,0.0386),
	resp.V = c(2.074, 2.075, 2.064, 2.076), 
	r2_threshold_smr = 0.9,
	path = "foldering",
	date_format = "y/m/d",
	N_Ch = 4,
	drop_ch = c(1))

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
	data.MMR = "none",
	data.SMR = "jul13_box2_rmr_26_analyzed.csv", 
	AnimalID = c("2604","2605", "2606", "2607"),
	BW.animal = c(0.0651,.0594,0.0367,0.0398),
	resp.V = c(2.079, 2.082, 2.074, 2.106), 
	r2_threshold_smr = 0.9,
	path = "foldering",
	date_format = "y/m/d",
	N_Ch = 4)

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
	data.MMR = "none",
	data.SMR = "jul13_box3_rmr_26_analyzed.csv", 
	AnimalID = c("2608","2609", NA,"2610"),
	BW.animal = c(0.0412,0.0278,NA,0.0243),
	resp.V = c(2.126, 2.060, NA, 2.070), 
	r2_threshold_smr = 0.9,
	path = "foldering",
	date_format = "y/m/d",
	N_Ch = 3)


```

North Umpqua
```{r}

#Ambient


#Box 1 - channel 4 is background
setwd(AUTO_csv_files)
SMR(data = "aug08_2022_box1_amb_rmr.csv",
    inventory_data = "inventory_steamboat_amb1.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders") #cleaned!

setwd(AUTO_csv_files)
SMR(data = "aug08_2022_box1_amb_rmr2.csv",
    # inventory_data =,
    cycle_start = 3,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders") #no cleaning necessary

setwd(AUTO_csv_files)
SMR(data = "aug08_2022_box1_amb_rmr3.csv",
    inventory_data = "inventory_steamboat_amb3.csv",
    cycle_start = 5,
    cycle_end = 15,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders") #cleaned!

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
  test = "none",
	data.MMR = "none",
	data.SMR = "aug08_2022_box1_amb_rmr_analyzed.csv", 
	AnimalID = c("A01","A02", "A03", NA),
	BW.animal = c(0.0143, 0.0146, 0.0136, NA),
	resp.V = c(2.086, 2.095, 2.089, 2.107), 
	r2_threshold_smr = 0.9,
	scaling_exponent_smr=1,
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4,
	drop_ch = 4)

#setwd("C:/Users/terra/Box Sync/SummerSteelhead_ThermalTolerance2/Umpqua/2022_SteamboatCreek/MMR_SMR_AS_EPOC/csv_input_files")
#MMR_SMR_AS_EPOC(
 # test = "none",
#	data.MMR = "none",
#	data.SMR = "aug08_2022_box1_amb_rmr2_analyzed.csv", 
#	AnimalID = c("A01","A02", "A03", NA),
#	BW.animal = c(0.0143, 0.0146, 0.0136, NA),
#	resp.V = c(2.086, 2.095, 2.089, 2.107), 
#	r2_threshold_smr = 0.9,
#	scaling_exponent_smr=1,
#	path = "foldering",
#	date_format = "m/d/y",
#	N_Ch = 4,
	#drop_ch = 4) #can't get this to run, but only 2 cycles so omitting

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
 test = "none",
	data.MMR = "none",
	data.SMR = "aug08_2022_box1_amb_rmr3_analyzed.csv", 
	AnimalID = c("A01","A02", "A03", NA),
	BW.animal = c(0.0143, 0.0146, 0.0136, NA),
	resp.V = c(2.086, 2.095, 2.089, 2.107), 
	r2_threshold_smr = 0.9,
	scaling_exponent_smr=1,
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4,
	drop_ch = c(4))



#Box 2 - channel 2 fish unwell, released
setwd(AUTO_csv_files)
SMR(data = "aug08_2022_box2_amb_rmr.csv",
    "inventory_steamboat_amb1.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders") #cleaned!

setwd(AUTO_csv_files)
SMR(data = "aug08_2022_box2_amb_rmr2.csv",
    "inventory_steamboat_amb2.csv",
    cycle_start = 3,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders") #cleaned!

setwd(AUTO_csv_files)
SMR(data = "aug08_2022_box2_amb_rmr3.csv",
    inventory_data = "inventory_steamboat_amb3.csv",
    cycle_start = 5,
    cycle_end = 15,
    chop_start = 60/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders") #cleaned!

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
  test = "none",
	data.MMR = "none",
	data.SMR = "aug08_2022_box2_amb_rmr_analyzed.csv", 
	AnimalID = c("A05","A06", "A07", "A08"),
	BW.animal = c(0.0097, NA, 0.0203, 0.0142),
	resp.V = c(2.095, NA, 2.095, 2.089), 
	scaling_exponent_smr=1,
	r2_threshold_smr = 0.9,
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4, drop_ch = c(2))

#setwd("C:/Users/terra/Box Sync/SummerSteelhead_ThermalTolerance2/Umpqua/2022_SteamboatCreek/MMR_SMR_AS_EPOC/csv_input_files")
#MMR_SMR_AS_EPOC(
 # test = "none",
#	data.MMR = "none",
#	data.SMR = "aug08_2022_box2_amb_rmr2_analyzed.csv", 
#	AnimalID = c("A05","A06", "A07", "A08"),
#	BW.animal = c(0.0097, 0, 0.0203, 0.0142),
#	resp.V = c(2.095, 2.094, 2.095, 2.089), 
#	scaling_exponent_smr=1,
#	r2_threshold_smr = 0.9,
#	path = "foldering",
#	date_format = "m/d/y",
#	N_Ch = 4, drop_ch = c(2))

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
  test = "none",
	data.MMR = "none",
	data.SMR = "aug08_2022_box2_amb_rmr3_analyzed.csv", 
	AnimalID = c("A05","A06", "A07", "A08"),
	BW.animal = c(0.0097, NA, 0.0203, 0.0142),
	resp.V = c(2.095, 2.094, 2.095, 2.089), 
	scaling_exponent_smr=1,
	r2_threshold_smr = 0.9,
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4, drop_ch=c(2))


#Box 3
setwd(AUTO_csv_files)
SMR(data = "aug08_2022_box3_amb_rmr.csv",
    "inventory_steamboat_amb1.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders")

setwd(AUTO_csv_files)
SMR(data = "aug08_2022_box3_amb_rmr2.csv",
 #  "inventory_steamboat_amb2.csv",
    cycle_start = 3,
    cycle_end = 10,
    chop_start = 0,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders") #no cleaning necessary

setwd(AUTO_csv_files)
SMR(data = "aug08_2022_box3_amb_rmr3.csv",
    inventory_data = "inventory_steamboat_amb3.csv",
    cycle_start = 5,
    cycle_end = 15,
    chop_start = 0,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders") #cleaned!


setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
  test = "none",
	data.MMR = "none",
	data.SMR = "aug08_2022_box3_amb_rmr_analyzed.csv", 
	AnimalID = c("A09","A010", "A11", "A12"),
	BW.animal = c(0.0158, 0.0114, 0.0181, 0.0186),
	resp.V = c(2.082, 2.088, 2.093, 2.091), 
	scaling_exponent_smr=1,
	r2_threshold_smr = 0.9,
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4)

#setwd("C:/Users/terra/Box Sync/SummerSteelhead_ThermalTolerance2/Umpqua/2022_SteamboatCreek/MMR_SMR_AS_EPOC/csv_input_files")
#MMR_SMR_AS_EPOC(
#  test = "none",
#	data.MMR = "none",
#	data.SMR = "aug08_2022_box3_amb_rmr2_analyzed.csv", 
#	AnimalID = c("A09","A010", "A11", "A12"),
#	BW.animal = c(0.0158, 0.0114, 0.0181, 0.0186),
#	resp.V = c(2.082, 2.088, 2.093, 2.091), 
#scaling_exponent_smr=1,
#	r2_threshold_smr = 0.9,
#	path = "foldering",
#	date_format = "m/d/y",
#	N_Ch = 4)

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
  test = "none",
	data.MMR = "none",
	data.SMR = "aug08_2022_box3_amb_rmr3_analyzed.csv", 
	AnimalID = c("A09","A010", "A11", "A12"),
	BW.animal = c(0.0158, 0.0114, 0.0181, 0.0186),
	resp.V = c(2.082, 2.088, 2.093, 2.091), 
	scaling_exponent_smr=1,
	r2_threshold_smr = 0.9,
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4)

#Climate

#Box 1
setwd(AUTO_csv_files)
SMR(data = "aug09_2022_box1_hot_rmr.csv", #ch4 is background
    inventory_data = "inventory_Steamboat.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders") #cleaned!

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
  test= "none",
	data.MMR = "none",
	data.SMR = "aug09_2022_box1_hot_rmr_analyzed.csv", 
	AnimalID = c("H01","H02", "H03", "H04"),
	BW.animal = c(0.0225, 0.0214, 0.0133, NA),
	resp.V = c(2.086, 2.095, 2.089, 2.107), 
	r2_threshold_smr = 0.9,
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4, drop_ch = 4)

#Box 2
setwd(AUTO_csv_files)
SMR(data = "aug09_2022_box2_hot_rmr.csv",
   inventory_data = "inventory_Steamboat.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders") 

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
  test= "none",
	data.MMR = "none",
	data.SMR = "aug09_2022_box2_hot_rmr_analyzed.csv", 
	AnimalID = c("H05","H06", "H07", "H08"),
	BW.animal = c(0.0135, 0.0191, 0.0221, 0.0351),
	resp.V = c(2.095, 2.094, 2.095, 2.089), 
	r2_threshold_smr = 0.9,
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4)

#Box3
setwd(AUTO_csv_files)
SMR(data = "aug09_2022_box3_hot_rmr.csv",
    inventory_data = "inventory_Steamboat.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders") #cleaned!

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
  test= "none",
	data.MMR = "none",
	data.SMR = "aug09_2022_box3_hot_rmr_analyzed.csv", 
	AnimalID = c("H09","H10", "H11", "H12"),
	BW.animal = c(0.0181, 0.0177, 0.0131, 0.0152),
	resp.V = c(2.082, 2.088, 2.093, 2.091), 
	r2_threshold_smr = 0.9,
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4)

#Intermediate - MMR temp 22C

#Box1
setwd(AUTO_csv_files)
SMR(data = "aug10_2022_box1_22_rmr.csv",
    inventory_data = "inventory_Steamboat.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders") #cleaned!

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
  test= "none",
	data.MMR = "none",
	data.SMR = "aug10_2022_box1_22_rmr_analyzed.csv", 
	AnimalID = c("I01","I02", "I03", "I04"),
	BW.animal = c(0.0421, 0.0165, 0.0321, NA),
	resp.V = c(2.086, 2.095, 2.089, 2.107), 
	r2_threshold_smr = 0.9,
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4, drop_ch = 4)

#Box2
setwd(AUTO_csv_files)
SMR(data = "aug10_2022_box2_22_rmr.csv",
    inventory_data = "inventory_Steamboat.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders") #cleaned!


setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
  test= "none",
	data.MMR = "none",
	data.SMR = "aug10_2022_box2_22_rmr_analyzed.csv", 
	AnimalID = c("I05","I06", "I07", "I08"),
	BW.animal = c(0.0342, 0.0198, 0.0166, 0.0133),
	resp.V = c(2.095, 2.094, 2.095, 2.089), 
	r2_threshold_smr = 0.9,
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4)

#Box3
setwd(AUTO_csv_files)
SMR(data = "aug10_2022_box3_22_rmr.csv",
    inventory_data = "inventory_Steamboat.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders") #cleaned!


setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
   test= "none",
	data.MMR = "none",
	data.SMR = "aug10_2022_box3_22_rmr_analyzed.csv", 
	AnimalID = c("I09","I10", "I11", "I12"),
	BW.animal = c(0.0143, 0.0117, 0.0098, 0.0119),
	resp.V = c(2.082, 2.088, 2.093, 2.091), 
	r2_threshold_smr = 0.9,
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4)

#Intermediate - MMR temp 19C

#Box1
setwd(AUTO_csv_files)
SMR(data = "aug11_2022_box1_19_rmr.csv",
   inventory_data = "inventory_Steamboat.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders") #cleaned!

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
  test= "none",
	data.MMR = "none",
	data.SMR = "aug11_2022_box1_19_rmr_analyzed.csv", 
	AnimalID = c("C01","C02", "C03", "C04"),
	BW.animal = c(0.0178, 0.0178, 0.0159, NA),
	resp.V = c(2.086, 2.095, 2.089, 2.107), 
	r2_threshold_smr = 0.9,
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4, drop_ch = 4)

#Box2
setwd(AUTO_csv_files)
SMR(data = "aug11_2022_box2_19_rmr.csv",
    inventory_data = "inventory_Steamboat.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders") #cleaned!


setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
   test= "none",
	data.MMR = "none",
	data.SMR = "aug11_2022_box2_19_rmr_analyzed.csv", 
	AnimalID = c("C05","C06", "C07", "C08"),
	BW.animal = c(0.0223, 0.0127, 0.0135, 0.0177),
	resp.V = c(2.095, 2.094, 2.095, 2.089), 
	r2_threshold_smr = 0.9,
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4)

#Box 3 

setwd(AUTO_csv_files)
SMR(data = "aug11_2022_box3_19_rmr.csv",
    inventory_data = "inventory_Steamboat.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders") #cleaned!

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
   test= "none",
	data.MMR = "none",
	data.SMR = "aug11_2022_box3_19_rmr_analyzed.csv", 
	AnimalID = c("C09","C10", "C11", "C12"),
	BW.animal = c(0.0133, 0.0143, 0.0108, 0.0118),
	resp.V = c(2.082, 2.088, 2.093, 2.091), 
	r2_threshold_smr = 0.9,
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4)


```

Siletz
```{r}

#Ambient Treatment

setwd(AUTO_csv_files)
SMR(data = "aug13_box1_rmr_amb.csv",
    inventory_data = "Gravel_Inventory.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders")

setwd(AUTO_csv_files)
SMR(data = "aug13_box2_rmr_amb.csv",
    inventory_data = "Gravel_Inventory.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders")

setwd(AUTO_csv_files)
SMR(data = "aug13_box3_rmr_amb.csv",
    inventory_data = "Gravel_Inventory.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders") #not using ch4, not enough good traces

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
	data.MMR = "none",
	data.SMR = "aug13_box1_rmr_amb_analyzed.csv", 
	AnimalID = c(NA,"G_A01", "G_A02", "G_A03"),
	BW.animal = c(NA,.0442,.0391, .0363),
	resp.V = c(2.074, 2.075, 2.064, 2.076), 
	r2_threshold_smr = 0.9,
	path = "foldering",
	drop_ch = c(1))

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
	data.MMR = "none",
	data.SMR = "aug13_box2_rmr_amb_analyzed.csv", 
	AnimalID = c("G_A04","G_A05", "G_A06", "G_A07"),
	BW.animal = c(.0226,.0163,.0217, .0212),
	resp.V = c(2.079, 2.082, 2.074, 2.106), 
	r2_threshold_smr = 0.9,
	r2_threshold_mmr = 0.9,
	path = "foldering",
	recovMMR_threshold = 0.5)

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
	data.MMR = "none",
	data.SMR = "aug13_box3_rmr_amb_analyzed.csv", 
	AnimalID = c("G_A08","G_A09", NA, "G_A10"),
	BW.animal = c(.0175,.0159,NA, .0132),
	resp.V = c(2.079, 1.59, 2.074, 1.59), 
	r2_threshold_smr = 0.9,
	r2_threshold_mmr = 0.9,
	path = "foldering",
	recovMMR_threshold = 0.5,
	drop_ch = c(3, 4))

#20-24 treatment

setwd(AUTO_csv_files)
SMR(data = "aug14_box1_rmr_22.csv",
    inventory_data = "Gravel_Inventory.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 30/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders")

setwd(AUTO_csv_files)
SMR(data = "aug14_box2_rmr_22.csv",
   inventory_data = "Gravel_Inventory.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 60/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders")

setwd(AUTO_csv_files)
SMR(data = "aug14_box3_rmr_22.csv",
    inventory_data = "Gravel_Inventory.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 60/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders")


setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
	data.MMR = "none",
	data.SMR = "aug14_box1_rmr_22_analyzed.csv", 
	AnimalID = c(NA,"G_2201", "G_2202", "G_2203"),
	BW.animal = c(NA,.0371,.0195, .0217),
	resp.V = c(2.074, 2.075, 2.064, 2.076), 
	r2_threshold_smr = 0.9,
	r2_threshold_mmr = 0.9,
	recovMMR_threshold = 0.5,
	path = "foldering",
	drop_ch = c(1))

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
	data.MMR = "none",
	data.SMR = "aug14_box2_rmr_22_analyzed.csv", 
	AnimalID = c("G_2204","G_2205", "G_2206", "G_2207"),
	BW.animal = c(.0323,.0213,.0313, .041),
	resp.V = c(2.079, 2.082, 2.074, 2.106), 
	r2_threshold_smr = 0.9,
	r2_threshold_mmr = 0.9,
		path = "foldering",
	recovMMR_threshold = 0.5)

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
	data.MMR = "none",
	data.SMR = "aug14_box3_rmr_22_analyzed.csv", 
	AnimalID = c("G_2208","G_2209", NA, "G_2210"),
	BW.animal = c(.0229,.0236,NA, .0151),
	resp.V = c(2.126, 2.205, NA, 2.25), 
	r2_threshold_smr = 0.9,
	r2_threshold_mmr = 0.9,
	recovMMR_threshold = 0.5,
		path = "foldering",
	drop_ch = c(3)) #keep ch4??? 

#18-22 treatment
setwd(AUTO_csv_files)
SMR(data = "aug15_box1_rmr_20.csv",
    inventory_data = "Gravel_Inventory.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 60/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders")

setwd(AUTO_csv_files)
SMR(data = "aug15_box2_rmr_20.csv",
    inventory_data = "Gravel_Inventory.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders")

setwd(AUTO_csv_files)
SMR(data = "aug15_box3_rmr_20.csv",
    inventory_data = "Gravel_Inventory.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders")

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
	data.MMR = "none",
	data.SMR = "aug15_box1_rmr_20_analyzed.csv", 
	AnimalID = c(NA,"G_1901", "G_1902", "G_1903"),
	BW.animal = c(NA,.0222, .0173, .0205),
	resp.V = c(2.074, 2.075, 2.064, 2.076), 
	r2_threshold_smr = 0.9,
	r2_threshold_mmr = 0.9,
	recovMMR_threshold = 0.5,
		path = "foldering",
	drop_ch = c(1))

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
	data.MMR = "none",
	data.SMR = "aug15_box2_rmr_20_analyzed.csv", 
	AnimalID = c("G_1904","G_1905", "G_1906", "G_1907"),
	BW.animal = c(.0278, .0215, .0201, .0266),
	resp.V = c(2.079, 2.082, 2.074, 2.106), 
	r2_threshold_smr = 0.9,
	r2_threshold_mmr = 0.9,
		path = "foldering",
	recovMMR_threshold = 0.5)

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
	data.MMR = "none",
	data.SMR = "aug15_box3_rmr_20_analyzed.csv", 
	AnimalID = c("G_1908","G_1909", NA, "G_1910"),
	BW.animal = c(.0177, .0295, NA, .0226),
	resp.V = c(2.126, 2.205, NA, 2.25), 
	r2_threshold_smr = 0.9,
	r2_threshold_mmr = 0.9,
		path = "foldering",
	recovMMR_threshold = 0.5,
	drop_ch = c(3))


#23-26 treatment
setwd(AUTO_csv_files)
SMR(data = "aug16_box1_rmr_24.csv",
    inventory_data = "Gravel_Inventory.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders")

setwd(AUTO_csv_files)
SMR(data = "aug16_box2_rmr_24.csv",
    inventory_data = "Gravel_Inventory.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 30/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders")

setwd(AUTO_csv_files)
SMR(data = "aug16_box3_rmr_24.csv",
    inventory_data = "Gravel_Inventory.csv",
    cycle_start = 4,
    cycle_end = 10,
    chop_start = 60/60,
    chop_end = 0/60,
    flush_plot = "OFF",
    N_Ch=4, path="UseFolders")

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
	data.MMR = "none",
	data.SMR = "aug16_box1_rmr_24_analyzed.csv", 
	AnimalID = c(NA,"G_2501", "G_2502", "G_2503"),
	BW.animal = c(NA,.0163, .0223, .0354),
	resp.V = c(2.074, 2.075, 2.064, 2.076), 
	r2_threshold_smr = 0.9,
	r2_threshold_mmr = 0.9,
	recovMMR_threshold = 0.5,
		path = "foldering",
	drop_ch = c(1))

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
	data.MMR = "none",
	data.SMR = "aug16_box2_rmr_24_analyzed.csv", 
	AnimalID = c("G_2504","G_2505", "G_2506", "G_2507"),
	BW.animal = c(.04, .0291, .0171, .0226),
	resp.V = c(2.079, 2.082, 2.074, 2.106), 
	r2_threshold_smr = 0.9,
	r2_threshold_mmr = 0.9,
		path = "foldering",
	recovMMR_threshold = 0.5,
	drop_ch = 2)

setwd(Analyzed_files)
MMR_SMR_AS_EPOC(
	data.MMR = "none",
	data.SMR = "aug16_box3_rmr_24_analyzed.csv", 
	AnimalID = c("G_2508","G_2509", NA, "G_2510"),
	BW.animal = c(.0188, .0221, NA, .0183),
	resp.V = c(2.126, 2.205, NA, 2.25), #remember to adjust as necessary
	r2_threshold_smr = 0.9,
	r2_threshold_mmr = 0.9,
	recovMMR_threshold = 0.5,
		path = "foldering",
	drop_ch = c(3))


```


#### 4. Metabolic Rate Analysis - Maximum Metabolic Rate (MMR)

```{r}

#Ambient Round 1 
setwd("C:/Users/terra/Box Sync/SummerSteelhead_ThermalTolerance2/John Day/2021_BridgeCreek/MANUAL/csv_files")
MMR(data.MMR = "jul13_box2_mmr_18.csv",
    cycles=3, 
    cycle_start=c(0.5, 9, 16),
    cycle_end=c(4, 12, 18.5),
    Ch1=0,Ch2=0,Ch3=1,Ch4=1, 
    clean_Ch1=c(0,0),
    clean_Ch2=c(0,0),
    clean_Ch3=c(0,0), 
    clean_Ch4=c(0,0),
    path = "Foldering",
    N_Ch = 4,
    date_format = "m/d/y")

setwd("C:/Users/terra/Box Sync/SummerSteelhead_ThermalTolerance2/John Day/2021_BridgeCreek/MANUAL/csv_files")
MMR(data.MMR = "jul13_box3_mmr_18.csv",
    cycles=2, 
    cycle_start=c(0, 8),
    cycle_end=c(3.8, 12),
    Ch1=0,Ch2=1,Ch3=1,Ch4=2, 
    clean_Ch1=c(0,0),
    clean_Ch2=c(0,0),
    clean_Ch3=c(0,0), 
    clean_Ch4=c(0,0),
    path = "Foldering",
    N_Ch = 4,
    date_format = "m/d/y")


setwd("C:/Users/terra/Box Sync/SummerSteelhead_ThermalTolerance2/John Day/2021_BridgeCreek/MMR_SMR_AS_EPOC/csv_input_files")
MMR_SMR_AS_EPOC(
	data.MMR = "jul13_box2_mmr_18_analyzed.csv",
	data.SMR = "none", 
	AnimalID = c(NA,NA, "A105", "A106"),
	BW.animal = c(NA,NA,.055,0.0591),
	resp.V = c(2.079, 2.082, 2.074, 2.106), 
	r2_threshold_smr = 0.9,
	r2_threshold_mmr = 0.9,
	recovMMR_threshold = 0.5,
	epoc_threshold = 1.2,
	end_EPOC_Ch = c(NA, NA, NA, NA),
	min_length_mmr = 120, 
	background_prior = NA,
	background_post = NA, 
	background_slope = NULL,
	background.V = NULL,
	MLND = FALSE,
	match_background_Ch = FALSE,
	mmr_background = "SAME_slope",
	path = "foldering",
	date_format = "y/m/d",
	N_Ch = 4,
	drop_ch = c(1,2))


setwd("C:/Users/terra/Box Sync/SummerSteelhead_ThermalTolerance2/John Day/2021_BridgeCreek/MMR_SMR_AS_EPOC/csv_input_files")
MMR_SMR_AS_EPOC(
	data.MMR = "jul13_box3_mmr_18_analyzed.csv",
	data.SMR = "none" , 
	AnimalID = c("A107","A108", "A109", "A110"),
	BW.animal = c(0.0241,0.0395,0.0533,0.0321),
	resp.V = c(2.126, 2.060, 2.07, 2.070), 
	r2_threshold_smr = 0.9,
	r2_threshold_mmr = 0.9,
	recovMMR_threshold = 0.5,
	epoc_threshold = 1.2,
	end_EPOC_Ch = c(NA, NA, NA, NA),
	min_length_mmr = 120, 
	background_prior = NA,
	background_post = NA, 
	background_slope = NULL,
	background.V = NULL,
	MLND = FALSE,
	match_background_Ch = FALSE,
	mmr_background = "SAME_slope",
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4,
	drop_ch = c(1))

#Ambient Round 2

setwd("C:/Users/terra/Box Sync/SummerSteelhead_ThermalTolerance2/John Day/2021_BridgeCreek/MANUAL/csv_files")
MMR(data.MMR = "jul15_box1_mmr_18.csv",
    cycles=4, 
    cycle_start=c(0, 8, 16, 24),
    cycle_end=c(4, 12,20,28),
    Ch1=0,Ch2=1,Ch3=1,Ch4=2, 
    clean_Ch1=c(0,0),
    clean_Ch2=c(0,0),
    clean_Ch3=c(0,0), 
    clean_Ch4=c(0,0),
    path = "Foldering",
    N_Ch = 4,
    date_format = "m/d/y")

setwd("C:/Users/terra/Box Sync/SummerSteelhead_ThermalTolerance2/John Day/2021_BridgeCreek/MANUAL/csv_files")
MMR(data.MMR = "jul15_box2_mmr_18.csv",
    cycles=4, 
    cycle_start=c(0, 8, 16, 24),
    cycle_end=c(3.5, 12,19.5,28),
    Ch1=1,Ch2=3,Ch3=2,Ch4=3, 
    clean_Ch1=c(0,0),
    clean_Ch2=c(0,0),
    clean_Ch3=c(0,0), 
    clean_Ch4=c(0,0),
    path = "Foldering",
    N_Ch = 4,
    date_format = "m/d/y")

#Channel 2 missed MMR?


setwd("C:/Users/terra/Box Sync/SummerSteelhead_ThermalTolerance2/John Day/2021_BridgeCreek/MANUAL/csv_files")
MMR(data.MMR = "jul15_box3_mmr_18.csv",
    cycles=2, 
    cycle_start=c(1.5, 8),
    cycle_end=c(6, 12),
    Ch1=1,Ch2=0,Ch3=0,Ch4=0, 
    clean_Ch1=c(0,0),
    clean_Ch2=c(0,0),
    clean_Ch3=c(0,0), 
    clean_Ch4=c(0,0),
    path = "Foldering",
    N_Ch = 4,
    date_format = "m/d/y")

#missed MMR on ch 2 and 4

setwd("C:/Users/terra/Box Sync/SummerSteelhead_ThermalTolerance2/John Day/2021_BridgeCreek/MMR_SMR_AS_EPOC/csv_input_files")
MMR_SMR_AS_EPOC(
	data.MMR = "jul15_box1_mmr_18_analyzed.csv",
	data.SMR = "none", 
	AnimalID = c(NA,"A201", "A202", "A203"),
	BW.animal = c(NA,0.0449,.0298,0.0332),
	resp.V = c(2.074, 2.075, 2.064, 2.076), 
	r2_threshold_smr = 0.9,
	r2_threshold_mmr = 0.9,
	recovMMR_threshold = 0.5,
	min_length_mmr = 120, 
	background_prior = NA,
	background_post = NA, 
	background_slope = NULL,
	background.V = NULL,
	MLND = FALSE,
	match_background_Ch = FALSE,
	mmr_background = "SAME_slope",
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4,
	drop_ch = c(1))

setwd("C:/Users/terra/Box Sync/SummerSteelhead_ThermalTolerance2/John Day/2021_BridgeCreek/MMR_SMR_AS_EPOC/csv_input_files")
MMR_SMR_AS_EPOC(
	data.MMR = "jul15_box2_mmr_18_analyzed.csv",
	data.SMR = "none", 
	AnimalID = c("A204","A205", "A206", "A207"),
	BW.animal = c(0.0364,.0274,0.0213, 0.0326),
	resp.V = c(2.079, 2.082, 2.074, 2.106), 
	r2_threshold_smr = 0.9,
	r2_threshold_mmr = 0.9,
	recovMMR_threshold = 0.5,
	min_length_mmr = 120, 
	background_prior = NA,
	background_post = NA, 
	background_slope = NULL,
	background.V = NULL,
	MLND = FALSE,
	match_background_Ch = FALSE,
	mmr_background = "SAME_slope",
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4)

setwd("C:/Users/terra/Box Sync/SummerSteelhead_ThermalTolerance2/John Day/2021_BridgeCreek/MMR_SMR_AS_EPOC/csv_input_files")
MMR_SMR_AS_EPOC(
	data.MMR = "jul15_box3_mmr_18_analyzed.csv",
	data.SMR = "none", 
	AnimalID = c("A208","A209", NA,"A210"),
	BW.animal = c(0.037,0.0189,NA,0.0562),
	resp.V = c(2.126, 2.060, NA, 2.070), 
	r2_threshold_smr = 0.9,
	r2_threshold_mmr = 0.9,
	recovMMR_threshold = 0.5,
	min_length_mmr = 120, 
	background_prior = NA,
	background_post = NA, 
	background_slope = NULL,
	background.V = NULL,
	MLND = FALSE,
	match_background_Ch = FALSE,
	mmr_background = "SAME_slope",
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 3)

#Moderate Treatment
setwd("C:/Users/terra/Box Sync/SummerSteelhead_ThermalTolerance2/John Day/2021_BridgeCreek/MANUAL/csv_files")
MMR(data.MMR = "jul16_box1_mmr_22.csv",
    cycles=4, 
    cycle_start=c(0, 8, 16, 24),
    cycle_end=c(4, 12,20,28),
    Ch1=0,Ch2=1,Ch3=1,Ch4=2, 
    clean_Ch1=c(0,0),
    clean_Ch2=c(0,0),
    clean_Ch3=c(0,0), 
    clean_Ch4=c(0,0),
    path = "Foldering",
    N_Ch = 4,
    date_format = "m/d/y")

setwd("C:/Users/terra/Box Sync/SummerSteelhead_ThermalTolerance2/John Day/2021_BridgeCreek/MANUAL/csv_files")
MMR(data.MMR = "jul16_box2_mmr_22.csv",
    cycles=4, 
    cycle_start=c(0, 8, 16, 24),
    cycle_end=c(4, 12,20,28),
    Ch1=1,Ch2=2,Ch3=2,Ch4=3, 
    clean_Ch1=c(0,0),
    clean_Ch2=c(10,14),
    clean_Ch3=c(0,0), 
    clean_Ch4=c(0,0),
    path = "Foldering",
    N_Ch = 4,
    date_format = "m/d/y")


setwd("C:/Users/terra/Box Sync/SummerSteelhead_ThermalTolerance2/John Day/2021_BridgeCreek/MANUAL/csv_files")
MMR(data.MMR = "jul16_box3_mmr_22.csv",
    cycles=2, 
    cycle_start=c(1.8, 8),
    cycle_end=c(5, 13.5),
    Ch1=1,Ch2=2,Ch3=0,Ch4=2, 
    clean_Ch1=c(0,0),
    clean_Ch2=c(0,0),
    clean_Ch3=c(0,0), 
    clean_Ch4=c(0,0),
    path = "Foldering",
    N_Ch = 4,
    date_format = "m/d/y")

setwd("C:/Users/terra/Box Sync/SummerSteelhead_ThermalTolerance2/John Day/2021_BridgeCreek/MMR_SMR_AS_EPOC/csv_input_files")
MMR_SMR_AS_EPOC(
	data.MMR = "jul16_box1_mmr_22_analyzed.csv",
	data.SMR = "none", 
	AnimalID = c(NA,"2201", "2202", "2203"),
	BW.animal = c(NA, 0.052, 0.0575, 0.0549),
	resp.V = c(2.074, 2.075, 2.064, 2.076), 
	r2_threshold_smr = 0.9,
	r2_threshold_mmr = 0.9,
	recovMMR_threshold = 0.5,
	epoc_threshold = 1.2,
	end_EPOC_Ch = c(NA, NA, NA, NA),
	min_length_mmr = 120, 
	background_prior = NA,
	background_post = NA, 
	background_slope = NULL,
	background.V = NULL,
	MLND = FALSE,
	match_background_Ch = FALSE,
	mmr_background = "SAME_slope",
	path = "foldering",
	date_format = "y/m/d",
	N_Ch = 4,
	drop_ch = c(1))

setwd("C:/Users/terra/Box Sync/SummerSteelhead_ThermalTolerance2/John Day/2021_BridgeCreek/MMR_SMR_AS_EPOC/csv_input_files")
MMR_SMR_AS_EPOC(
	data.MMR = "jul16_box2_mmr_22_analyzed.csv",
	data.SMR = "none", 
	AnimalID = c("2204","2205", "2206", "2207"),
	BW.animal = c(0.0446, 0.045, 0.0314, 0.0296),
	resp.V = c(2.079, 2.082, 2.074, 2.106), 
	r2_threshold_smr = 0.9,
	r2_threshold_mmr = 0.9,
	recovMMR_threshold = 0.5,
	epoc_threshold = 1.2,
	end_EPOC_Ch = c(NA, NA, NA, NA),
	min_length_mmr = 120, 
	background_prior = NA,
	background_post = NA, 
	background_slope = NULL,
	background.V = NULL,
	MLND = FALSE,
	match_background_Ch = FALSE,
	mmr_background = "SAME_slope",
	path = "foldering",
	date_format = "y/m/d",
	N_Ch = 4)

setwd("C:/Users/terra/Box Sync/SummerSteelhead_ThermalTolerance2/John Day/2021_BridgeCreek/MMR_SMR_AS_EPOC/csv_input_files")
MMR_SMR_AS_EPOC(
	data.MMR = "jul16_box3_mmr_22_analyzed.csv",
	data.SMR = "none", 
	AnimalID = c("2208","2209", NA,"2210"),
	BW.animal = c(0.0309, 0.0262, NA, 0.0254),
	resp.V = c(2.126, 2.060, NA, 2.070), 
	r2_threshold_smr = 0.9,
	r2_threshold_mmr = 0.9,
	recovMMR_threshold = 0.5,
	epoc_threshold = 1.2,
	end_EPOC_Ch = c(NA, NA, NA, NA),
	min_length_mmr = 120, 
	background_prior = NA,
	background_post = NA, 
	background_slope = NULL,
	background.V = NULL,
	MLND = FALSE,
	match_background_Ch = FALSE,
	mmr_background = "SAME_slope",
	path = "foldering",
	date_format = "y/m/d",
	N_Ch = 3)

#Hot Treatment

setwd("C:/Users/terra/Box Sync/SummerSteelhead_ThermalTolerance2/John Day/2021_BridgeCreek/MANUAL/csv_files")
MMR(data.MMR = "jul14_box1_mmr_26.csv",
    cycles=4, 
    cycle_start=c(0.2, 8, 16, 24),
    cycle_end=c(4, 11.3,19.3,28),
    Ch1=0,Ch2=1,Ch3=1,Ch4=2, 
    clean_Ch1=c(0,0),
    clean_Ch2=c(0,0),
    clean_Ch3=c(0,0), 
    clean_Ch4=c(0,0),
    path = "Foldering",
    N_Ch = 4,
    date_format = "m/d/y")

setwd("C:/Users/terra/Box Sync/SummerSteelhead_ThermalTolerance2/John Day/2021_BridgeCreek/MANUAL/csv_files")
MMR(data.MMR = "jul14_box2_mmr_26.csv",
    cycles=4, 
    cycle_start=c(0.2, 8, 16, 26.3),
    cycle_end=c(3.5, 12,20,30),
    Ch1=1,Ch2=2,Ch3=2,Ch4=3, 
    clean_Ch1=c(0,0),
    clean_Ch2=c(0,0),
    clean_Ch3=c(0,0), 
    clean_Ch4=c(0,0),
    path = "Foldering",
    N_Ch = 4,
    date_format = "m/d/y")


setwd("C:/Users/terra/Box Sync/SummerSteelhead_ThermalTolerance2/John Day/2021_BridgeCreek/MANUAL/csv_files")
MMR(data.MMR = "jul14_box3_mmr_26.csv",
    cycles=2, 
    cycle_start=c(0, 12),
    cycle_end=c(5, 16),
    Ch1=1,Ch2=2,Ch3=0,Ch4=2, 
    clean_Ch1=c(3.5,5),
    clean_Ch2=c(0,0),
    clean_Ch3=c(0,0), 
    clean_Ch4=c(0,0),
    path = "Foldering",
    N_Ch = 4,
    date_format = "m/d/y") #re-check these. Not sure if can use last couple MMRs

setwd("C:/Users/terra/Box Sync/SummerSteelhead_ThermalTolerance2/John Day/2021_BridgeCreek/MMR_SMR_AS_EPOC/csv_input_files")
MMR_SMR_AS_EPOC(
	data.MMR = "jul14_box1_mmr_26_analyzed.csv",
	data.SMR = "none", 
	AnimalID = c(NA,"2601", "2602", "2603"),
	BW.animal = c(NA,0.0348,.0789,0.0386),
	resp.V = c(2.074, 2.075, 2.064, 2.076), 
	r2_threshold_smr = 0.9,
	r2_threshold_mmr = 0.9,
	recovMMR_threshold = 0.5,
	min_length_mmr = 120, 
	background_prior = NA,
	background_post = NA, 
	background_slope = NULL,
	background.V = NULL,
	MLND = FALSE,
	match_background_Ch = FALSE,
	mmr_background = "SAME_slope",
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4,
	drop_ch = c(1))

setwd("C:/Users/terra/Box Sync/SummerSteelhead_ThermalTolerance2/John Day/2021_BridgeCreek/MMR_SMR_AS_EPOC/csv_input_files")
MMR_SMR_AS_EPOC(
	data.MMR = "jul14_box2_mmr_26_analyzed.csv",
	data.SMR = "none", 
	AnimalID = c("2604","2605", "2606", "2607"),
	BW.animal = c(0.0651,0.0367,.0594,0.0398),
	resp.V = c(2.079, 2.082, 2.074, 2.106), 
	r2_threshold_smr = 0.9,
	r2_threshold_mmr = 0.9,
	recovMMR_threshold = 0.5,
	min_length_mmr = 120, 
	background_prior = NA,
	background_post = NA, 
	background_slope = NULL,
	background.V = NULL,
	MLND = FALSE,
	match_background_Ch = FALSE,
	mmr_background = "SAME_slope",
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4)

setwd("C:/Users/terra/Box Sync/SummerSteelhead_ThermalTolerance2/John Day/2021_BridgeCreek/MMR_SMR_AS_EPOC/csv_input_files")
MMR_SMR_AS_EPOC(
	data.MMR = "jul14_box3_mmr_26_analyzed.csv",
	data.SMR = "none", 
	AnimalID = c("2608","2609", NA,"2610"),
	BW.animal = c(0.0412, 0.0278, NA, 0.0243),
	resp.V = c(2.126, 2.060, NA, 2.070), 
	r2_threshold_smr = 0.9,
	r2_threshold_mmr = 0.87,
	recovMMR_threshold = 0.5,
	min_length_mmr = 120, 
	background_prior = NA,
	background_post = NA, 
	background_slope = NULL,
	background.V = NULL,
	MLND = FALSE,
	match_background_Ch = FALSE,
	mmr_background = "SAME_slope",
	path = "foldering",
	date_format = "m/d/y",
	N_Ch = 4, drop_ch = c(3))

```

