---
title: "0_Scaling_Metabolic_Rate"
author: "Terra Dressler"
date: "2024-05-09"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

This RMD contains analysis that generated body weight scaling exponents for juvenile O. mykiss metabolic rate data. Metabolic rate data from 4 populations of Oregon O. mykiss and 2 populations of California O.mykiss (from Dressler et al. 2023; https://doi.org/10.1038/s41598-023-41173-7). 

The following analysis generates mass scaling exponents for maximum metabolic rate (MMR) and for resting (or routine) metabolic rate(RMR).

#### Libraries

```{r}

library(tidyverse)
library(lme4)
library(ggpubr)

```


#### Mass Scaling: Maximum Metabolic Rate (MMR)

```{r}

#Step 1: Load Data

MMR_LD <- read_csv("MMR_LowerDeschutes.csv")
MMR_JD <- read_csv("MMR_JohnDay.csv")
MMR_NU <- read_csv("MMR_NorthUmpqua.csv")
MMR_S <- read_csv("MMR_Siletz.csv")
MMR_CA <- read_csv("MMR_California.csv")

MMR_All <- rbind(MMR_LD, MMR_JD, MMR_NU, MMR_S, MMR_CA)

#Step 2: plot unscaled MMR values on a log-log scale

ggplot(MMR_All, aes(x = log10(bw), y = log10(mmr_unscaled), color = population))+
  geom_point()+
  theme_classic()+
  labs(x = "Log Body Weight (kg)", y = "Log MMR (mgO2/min)")+
  theme(text = element_text(size = 14))

ggplot(MMR_All, aes(x = log10(bw), y = log10(mmr_unscaled), color = temperature))+
  geom_point()+
  theme_classic()+
  labs(x = "Log Body Weight (kg)", y = "Log MMR (mgO2/min)")+
  theme(text = element_text(size = 14))

#Step 3: model fitting

MMR_no_scaling <- lm(log10(mmr_unscaled)~1, data = MMR_All)
MMR_isometric <- lm(log10(mmr_unscaled)~offset(1*log10(bw)), data = MMR_All)
MMR_allometric_89 <- lm(log10(mmr_unscaled)~offset(0.89*log10(bw)), data = MMR_All)
MMR_allometric_data <- lm(log10(mmr_unscaled)~log10(bw), data = MMR_All)
MMR_allometric_site <- lm(log10(mmr_unscaled)~log10(bw) + population, data = MMR_All) #best
MMR_allometric_site2 <- lm(log10(mmr_unscaled)~log10(bw) * population, data = MMR_All)
MMR_allometric_Temp <- lm(log10(mmr_unscaled)~log10(bw) + temperature, data = MMR_All)
MMR_allometric_Temp2 <- lm(log10(mmr_unscaled)~log10(bw) * temperature, data = MMR_All)

BIC(MMR_no_scaling, MMR_isometric,MMR_allometric_89, MMR_allometric_data , MMR_allometric_site,MMR_allometric_site2, MMR_allometric_Temp, MMR_allometric_Temp2)

summary(MMR_allometric_site) #scaling exponent: 0.74



```


#### Mass Scaling: Resting Metabolic Rate (RMR)

```{r}

#Step 1: Load Data

RMR_LD <- read_csv("RMR_LowerDeschutes.csv") %>% 
  select(fish_id, treatment,temp,mean_rmr_unscaled,bw) %>% 
  mutate(population="Lower Deschutes", fish_id=paste0("LD_", fish_id))
RMR_JD <- read_csv("RMR_JohnDay.csv") %>% 
  select(fish_id, treatment,temp,mean_rmr_unscaled,bw) %>% 
  mutate(population="John Day", fish_id=paste0("JD_", fish_id))
RMR_NU <- read_csv("RMR_NorthUmpqua.csv") %>%
  select(fish_id, treatment,temp,mean_rmr_unscaled,bw) %>% 
  mutate(population="North Umpqua", fish_id=paste0("NU_", fish_id))
RMR_S <- read_csv("RMR_Siletz.csv") %>% 
  select(fish_id, treatment,temp,mean_rmr_unscaled,bw) %>% 
  mutate(population="Siletz", fish_id=paste0("S_", fish_id))
RMR_CA <- read_csv("RMR_California.csv") %>% 
  filter(n>2) %>% 
  select(fish_id, treatment,temp,mean_rmr_unscaled, population,bw)

RMR_All <- rbind(RMR_LD, RMR_JD, RMR_NU, RMR_S, RMR_CA)

#Step 2: plot unscaled RMR values on a log-log scale

ggplot(RMR_All, aes(x = log10(bw), y = log10(mean_rmr_unscaled)))+
  geom_point()+
  theme_classic()+
  labs(x = "Log Body Weight (kg)", y = "Log RMR (mgO2/min)")+
  theme(text = element_text(size=14))+
  stat_smooth(method="lm")+
  stat_regline_equation()

ggplot(RMR_All, aes(x = log10(bw), y = log10(mean_rmr_unscaled), color = population))+
  geom_point()+
  theme_classic()+
  labs(x = "Log Body Weight (kg)", y = "Log RMR (mgO2/min)")+
  theme(text = element_text(size=14))

ggplot(RMR_All, aes(x = log10(bw), y = log10(mean_rmr_unscaled), color = temp))+
  geom_point()+
  theme_classic()+
  labs(x = "Log Body Weight (kg)", y = "Log RMR (mgO2/min)")+
  theme(text = element_text(size=14))

#Model fitting: using linear mixed models to account for repeated measures of individual fish

RMR_no_scaling <- lmer(log10(mean_rmr_unscaled)~1 + (1|fish_id), data = RMR_All)
RMR_isometric <- lmer(log10(mean_rmr_unscaled)~offset(1*log10(bw))+ (1|fish_id), data = RMR_All)
RMR_allometric_89 <- lmer(log10(mean_rmr_unscaled)~offset(0.89*log10(bw))+ (1|fish_id), data = RMR_All)
RMR_allometric_data <- lmer(log10(mean_rmr_unscaled)~log10(bw)+ (1|fish_id), data = RMR_All)
RMR_allometric_site <- lmer(log10(mean_rmr_unscaled)~log10(bw) + population+ (1|fish_id), data =RMR_All)
RMR_allometric_site2 <- lmer(log10(mean_rmr_unscaled)~log10(bw) * population+ (1|fish_id), data = RMR_All)
RMR_allometric_Temp <- lmer(log10(mean_rmr_unscaled)~log10(bw) + temp +(1|fish_id), data = RMR_All)
RMR_allometric_Temp2 <- lmer(log10(mean_rmr_unscaled)~log10(bw) * temp + (1|fish_id), data = RMR_All)
RMR_allometric_site_temp <- lmer(log10(mean_rmr_unscaled)~log10(bw) + temp + population+ (1|fish_id), data = RMR_All) #best
RMR_allometric_site_temp2 <- lmer(log10(mean_rmr_unscaled)~log10(bw) * temp * population+ (1|fish_id), data = RMR_All)
RMR_allometric_site_temp4 <- lmer(log10(mean_rmr_unscaled)~log10(bw) * temp + population+ (1|fish_id), data = RMR_All)#best2

BIC(RMR_no_scaling, RMR_isometric,RMR_allometric_89, RMR_allometric_data , RMR_allometric_site,RMR_allometric_site2, RMR_allometric_Temp, RMR_allometric_Temp2, RMR_allometric_site_temp, RMR_allometric_site_temp2, RMR_allometric_site_temp4)

BIC(RMR_allometric_site_temp, RMR_allometric_site_temp4)

summary(RMR_allometric_site_temp) #scaling exponent = 0.72

summary(RMR_allometric_site_temp4) #interaction is weak (0.019991), but present and positive. Evidence of constrained scope with body size for this species??? Slope gets steeper as temperature gets warmer. BIC comparisons justify using 1 scaling exponent (within BIC delta 7)

```

